Title Goes Here \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2021-04-13 analysis/paper/shceof.Rmd
Renderiza todo

  geom_smooth(data = ~qwrap(.x, arg = c(-pi, pi) ~ c(-2*pi, 2*pi)),
              method = "lm", aes(weight = mag),
              formula = y ~ I(sin(x)) + I(cos(x)) -1,
              se = FALSE, color = "black", size = 0.5) +
    geom_point(aes(colour = mag >= quantile(mag, 0.5),
                 shape  = mag >= quantile(mag, 0.5)),
             size = 3) +

>>>>

  geom_smooth(data = ~qwrap(.x, arg = c(-pi, pi) ~ c(-2*pi, 2*pi)),
              method = "lm", aes(weight = mag),
              formula = y ~ I(sin(x)) + I(cos(x)) -1,
              se = FALSE, color = "black", size = 0.5, 
              fullrange = TRUE) +
    geom_point(aes(colour = mag >= quantile(mag, 0.5),
                 shape  = mag >= quantile(mag, 0.5)),
             size = 3) +

### 2021-04-13 analysis/paper/shceof.tex
Renderiza todo

\textcolor{red}{Creo que habría que expandir un poco esta parte e ir comentando todoas las metodologías que vas usando: regresiones, tendencias, cómo evlauas significancia en cada caso, etc. }

>>>>

We performed linear regressions to quantify the association between the cEOFs and other variables. For each cEOF, we create regression maps by computing fitting a multiple linear model involving both the real and the imaginary part. We evaluated statistical significance using a two-sided t-test and, in the case of regression maps, p-values were adjusted by controlling for the False Discovery Rate \citep{benjamini1995, wilks2016} to avoid misleading results from the high number of regressions \citep{walker1914, katz1991}.

Linear trends were computed by Ordinary Least Squares and the 95\% confidence interval was computed assuming a t-distribution with the appropriate residual degrees of freedom. To the amplitude of the zonal waves is defined through computing the Fourier transform of the spatial field at each latitude circle.
